\documentstyle[hyperref,margin,line]{res_yy}
\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\renewcommand{\namefont}{\LARGE\emph}
\begin{document}
\name{Dan Hirsch}
\address{
Rue Notre Dame du Sommeil 24\\
1000 Brussels\\
Belgium\hskip 9em thequux@gmail.com
}

\begin{resume}
\section{\textsc{Computer and Programming Experience}}
\begin{itemize}
\item{} Experience designing application-specific microcontroller boards
\item{} Comfortable writing and debugging Linux USB drivers and embedded firmware
\item{} Production of user-mode and kernel-mode drivers for both Linux and my hobby OS
\item{} Fluency in low-level programming with Assembly, C, C++, and Go
\item{} Creation of small Linux environments for specialized purposes, such as driver testing and net booting for installs
\item{} Database performance optimization with PostgreSQL
\item{} Usage of Common Lisp, Perl, Python, PHP for rapid development
\item{} Troubleshooting software issues using tracing and monitoring tools.
\item{} Creation of distributable desktop programs using C\#, Java
\item{} Development of web applications using JavaScript, jQuery, and CherryPy
\item{} Programming user interfaces using GTK+, CLIM
\item{} Experience with version control using CVS, SVN, Bazaar, Mercurial, and Git
\item{} Proficiency in programming and administrating Linux/POSIX and .NET CLR environments
\item{} Construction of build systems using Make and GNU LD scripts
\end{itemize}

\section{\textsc{Employment Experience}}
\begin{formatb}
  \employer{l}\title{r}\\
  \location{l}\dates{r}\\
  \body\\
\end{formatb}

\employer{\textbf{Google, Inc.}}
\title{Site Reliability Engineer}
\location{Mountain View, CA}
\dates{2010 -- 2011}
\begin{position}
  Worked with a team of eight people to run a low-latency, highly
  available planet-scale storage system for petabytes of data.
  Debugged production issues including fiber cuts, misbehaving
  clients, heavy resource contention, and hardware failure.
  Participated in weekly on-call rotation, with an SLA requiring a
  five-minute response time.  Helped internal clients get started
  using our service.  Led project to automate deployment of new
  versions of our service across dozens of clusters; reduced SRE time
  spent on weekly pushes by 90\%.  Supported Cellbots project in 20\%
  time.  Assisted with design of the ``IOIO'' I/O board for Android.
\end{position}

\employer{\textbf{Flippity.com}}
\title{Co-founder}
\dates{2009 -- 2010}
\begin{position}
  Wrote and optimized backend for Craigslist and eBay search site
  using Python and PostgreSQL.  Wrote core of distributed scraping
  tool using a Java applet with a Python server component.
  Implemented the use of Gerrit for code reviews.
\end{position}

\employer{\textbf{Law Firm of Moreno, Becerra, and Casillas}}
\title{System Administrator}
\dates{2009}
\location{Los Angeles, CA}
\begin{position}
  Maintenance and operation of a network of two Windows servers
  serving twenty Windows clients as sole systems administrator, with
  responsibility for all network services, including Exchange and
  Active Directory.  Resolved various systems issues such as Android
  clients being unable to fetch email; implemented Postini email
  filtering.
\end{position}

\employer{\textbf{Google, Inc.}}
\title{Systems Administration Intern}
\dates{2008}
\location{Santa Monica, CA}
\begin{position}
  Supported Linux kernel for internal workstation use.  Debugged
  workaround in kernel for NFS group count limitation using
  KDB. Helped develop on-disk format for the TUX3 fourth- generation
  Linux file system.  Suggested and investigated switching to GIT for
  internal version-control.  Debugged Kerberos/LDAP integration on
  Google’s corporate WAN.
\end{position}

\employer{\textbf{University of California at Los Angeles}}
\title{Laboratory Assistant III}
\dates{2007 -- 2008}
\location{Los Angeles, CA}
\begin{position}
  Wrote kernel-mode drivers for specialized video coding hardware on a
  custom ST40-based board running embedded Linux for an
  industry-funded project seeking to develop a peer-to- peer streaming
  video system similar to BitTorrent.
\end{position}

\employer{\textbf{Northrop Grumman Corporation, Space \& Technology Sector}}
\title{Intern}
\dates{2006 -- 2007}
\location{Los Angeles, CA}
\begin{position}
  Worked on design and implementation of a reliability calculation
  software package for internal use.  Wrote tool to allow remote
  dialing of Cisco VOIP telephones from Microsoft Outlook 2003.
  Compared derating and Digital IC/Hybrid part specifications.
\end{position}

\section{\textsc{Personal Projects}}
\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\employer{\textbf{Co-developer of GoodFET}}
\dates{2010 -- Present}
\begin{position}
  Implemented Atmel AVR target support.  Added support for certain
  subfamilies of Microchip PIC24F chips.  Designed and evaluated new
  board design based on TI Stellaris LM3S3739 microprocessor.
  Designed new board variant based on TI MSP430F5510 microcontroller;
  reduced cost by 50\% and component count by 10\%.
\end{position}

\employer{\textbf{System Administrator for UCLA Linux Users' Group}}
\dates{2007 -- 2010}
\begin{position}
  Administered two servers for the UCLA LUG, with responsibility for
  email, web, shell, network authentication, server configuration, and
  administration procedures.  Implemented Kerberos authentication.
  Initiated documentation of system design and operating procedures.
\end{position}

\employer{\textbf{Tutorials for UCLA CS152B – Digital Logic Design Lab}}
\dates{Fall 2008}
\begin{position}
  Created a pair of tutorials for developing hardware systems on the
  Digilent XUPV2P Virtex 2 Pro evaluation board, covering interfacing
  custom hardware with the built-in PowerPC 405 processor cores and
  interfacing with the onboard AC’97 audio codec.  These tutorials are
  currently used by the UCLA Computer Science Department as course
  instruction materials.
\end{position}

\employer{\textbf{Postscript extensions for programming use}}
\dates{Fall 2008}
\begin{position}
  Used PostScript reflection to add several higher-order functions to
  the language, including function currying, composition, Factor-style
  ``cleave,'' ``keep,'' and ``bi'' operators.  Also developed sample
  unit testing framework.  Presented demo as a technical talk to the
  Southern California Functional Programmers group in November, 2008.
\end{position}

\employer{\textbf{Xenon OS -- An Original X86 Protected-Mode Kernel}}
\dates{2006 -- 2007}
\begin{position}
  Developed a partial protected-mode kernel that handles basic memory
  management, keyboard, basic disk, and PCI bus access, and supports
  both Cirrus Logic CL-5446 and VMware built-in framebuffer devices to
  display high-resolution text and graphics.  Makes limited use of
  APM.
\end{position}

\subsection{\textsc{Miscellaneous Hacks and Small-Scale Projects}}
\begin{itemize}
\item Monad tutorial for O’Caml
\item libusb-1.0 bindings for Go
\item Testing framework for Prolog
\item MSP430 BSLv2 client in Go
\item Tool for plotting filesystem fragmentation
\item Generic constraint-satisfaction problem solver using C and
  Python with pluggable search strategies in Haskell
\item EWMH strut support for xbattbar
\end{itemize}

\section{\textsc{Project Team Experience}}
\begin{formatb}
  \employer{l}\dates{r}\\
  \location{l}\\
  \body\\
\end{formatb}

\employer{\textbf{Terra Engineering}}
\dates{2005 -- 2006}
\location{\textit{Autonomous vehicle designed and built for the 2005 DARPA Grand Challenge}}
\begin{position}
  Wrote code to parse the DARPA-provided “Route Definition Data File.”
  Worked on obstacle tracking and mapping module and Athena sensor
  support.  Developed various stereo vision algorithms.  Fixed LIDAR
  issues, including incorrect documentation and driver bugs.  Rewrote
  monitor to use GTK+ toolkit, improving flexibility.  Wrote a variety
  of system monitoring/management and data processing scripts.
\end{position}

\employer{\textbf{Project Grant Proposal}}
\dates{Winter 2005}
\location{\textit{Research Proposal for Microsoft’s External Research Digital Inclusion Program}}
\begin{position}
  Researched feasibility and prior art for the design and
  implementation of a small IDE on the Pocket PC platform for
  submission with Dr. Massoud Ghyam.
\end{position}

\employer{\textbf{Palos Verdes Road Warriors}}
\dates{2002 -- 2003}
\location{\textit{Autonomous vehicle modified from SUV for 2003 DARPA Grand Challenge}}
\begin{position}
  Worked with a software tool called ``RVCad'' to find optimal
  parameters and filters for preprocessing an image for input to a
  road-finding algorithm. Wrote test code to get the vehicle control
  actuators to work; this test code became a simple closed-loop speed
  control system. Also wrote init scripts to automatically start the
  custom servers. Debugged LIDAR and GPS systems.
\end{position}

\section{\textsc{Education}}
\begin{formatb}
  \employer{l}\dates{r}\\
  %\title{l}\location{r}\\
  \body\\
\end{formatb}

\employer{\textbf{University of California, Los Angeles}}
\dates{2006-2009}
\title{\relax}
\location{\relax}
\begin{position}
  Completed 143 units toward Bachelor of Science degrees in Electrical
  Engineering and Computer Science.

 Coursework included:
  \begin{description}
  \item[Computer Science 111] Operating System Principles
  \item[Computer Science 131] Programming Languages
  \item[Computer Science 132] Compilers
  \item[Computer Science 151] Computer Architecture
  \item[Computer Science 152B] Advanced Logic Design Lab
  \item[Computer Science 180] Algorithms
  \item[Computer Science 181] Formal Languages and Automata Theory
  \item[Math 113] Combinatorics
  \item[Math 199] Variable Topics, Algorithms
  \end{description}
\end{position}

\employer{\textbf{Stanford EPGY}}
%\title{\textit{Distance education offered by Stanford University for college credit}}
\dates{2005 -- 2006}
\location{\textit{Concurrent with high-school enrollment}}
\begin{position}
  \vspace{-1em}
  \begin{itemize}
  \item Linear Algebra
  \item Ordinary Differential Equations
  \end{itemize}
\end{position}

\employer{\textbf{El Camino College}}
\title{\relax}
\dates{2003 -- 2006}
\location{\textit{Concurrent with high-school enrollment}}
\begin{position}
  Math/engineering coursework included:
  \begin{description}
  \item[Computer Science 1] Problem Solving and Program Design in C++ 
  \item[Computer Science 2] Data Structures
  \item[Math 210] Discrete Structures
  \item[Math 220] Multi-Variable Calculus
  \end{description}    
\end{position}

\employer{\textbf{Palos Verdes Peninsula High School}}
\dates{2002 -- 2006}
\location{\relax}
\title{\relax}
\begin{position}
  \relax
\end{position}

\end{resume}
\end{document}
